### 2015-07-09 2015-compmorphon-morphver/poster.tex
more layout and stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61228 72bbbca6-d526-0410-a7d9-f06f51895060

	\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=tuvanvelars}{
		%\begin{itemize}
			%\item Disambiguation, more stems, clean up transducers
			%\item Machine translation between these languages
			%\item Bring other Kypchak transducers to comparable performance:\\
			%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
			%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
		%\end{itemize}
	}

	\headerbox{Further information}{name=getting,column=2,below=nedostatki}{
		\begin{itemize}
			\item Part of \textbf{Apertium Turkic} project:\\
			\url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
			\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
			\item \textbf{Source code} available from Apertium's SVN repo
			%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Turkic RBMT \textbf{mailing list} (>25 subscribers):\\
			\texttt{apertium-turkic@lists.sourceforge.net}\\
			\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
			\item And feel free to contact the authors any time!
		\end{itemize}
		\tikzoverlay[text width=0.8in] at (2.85in, 0.77in) {
			\includegraphics[height=0.8in]{qrcode}
		};
	}

@@

			\scalebox{0.83}{
				\begin{tabular}{lllll}
					\toprule
					\textbf{Type} & \textbf{Gloss} & {\small \texttt{\tag{adj}(\tag{comp})}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{subst}}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{advl}}} \\
					\midrule
					\textbf{A1} & \eng{good} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} \\
					\textbf{A2} & \eng{old} & {\qipa иске (искерәк)} & {\qipa иске (искерәк)} & {\qipa — (—)} \\
					\textbf{A3} & \eng{dead} & {\qipa үле (—)} & {\qipa үле (—)} & {\qipa — (—)} \\
					\textbf{A4} & \eng{basic} & {\qipa төп (—)} & {\qipa — (—)} & {\qipa — (—)} \\
					\bottomrule
				\end{tabular}
			}\\
			\begin{itemize}
				\item Interestingly, native-speaker intuitions on the morphological limitations of a given adjective can often be more restrictive than the range of possible uses found in a large text corpus.
			\end{itemize}
	}

@@

		\headerbox{References}{name=references,column=1,below=tuvanvelars}{
			\begin{spacing}{0.75}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-0.3em}
		}

>>>>

@@

			\scalebox{0.83}{
				\begin{tabular}{lllll}
					\toprule
					\textbf{Type} & \textbf{Gloss} & {\small \texttt{\tag{adj}(\tag{comp})}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{subst}}} & {\small \texttt{\tag{adj}(\tag{comp})\tag{advl}}} \\
					\midrule
					\textbf{A1} & \eng{good} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} & {\qipa яхшы (яхшырак)} \\
					\textbf{A2} & \eng{old} & {\qipa иске (искерәк)} & {\qipa иске (искерәк)} & {\qipa — (—)} \\
					\textbf{A3} & \eng{dead} & {\qipa үле (—)} & {\qipa үле (—)} & {\qipa — (—)} \\
					\textbf{A4} & \eng{basic} & {\qipa төп (—)} & {\qipa — (—)} & {\qipa — (—)} \\
					\bottomrule
				\end{tabular}
			}\\
			\begin{itemize}
				%\item Interestingly, native-speaker intuitions on the morphological limitations of a given adjective can often be more restrictive than the range of possible uses found in a large text corpus.
				\item Native speaker intuitions on morph.\ limitations often more restrictive than range of possible uses found in large text copora.
			\end{itemize}
	}

@@

		\headerbox{References}{name=references,column=1,below=tuvanvelars}{
			\begin{spacing}{0.75}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-0.2em}
		}

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=tuvanvelars}{
		\begin{itemize}
				\item Fixing morphology and disambiguation by developing a dependency treebank for Kazakh
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
			\end{itemize}
		}

		\headerbox{Further information}{name=getting,column=2,below=adjectives,span=2}{
			%\vspace{-0.2em}
			\tikzoverlay[text width=0.8in] at (6.73in, 0.04in) {
				\includegraphics[height=0.8in]{qrcode}
			};
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} (\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}), \textbf{source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
		}
